When are Fuzzy Extractors Possible?

### 2014-10-07 trunk/info-bounds/FuzzyExtPossibility.tex
minor cleanup of distribution aware setting

\paragraph{The Case of Known Distribution}
If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.  In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{If we wish to be pedantic and extend correctness to all of $\mathcal{M}$, we can define $\gen$/$\sketch$ to be the identity function on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this will not harm security}.

>>>>

\paragraph{The Case of Known Distribution}
If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.  In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not effect security.}.
